Exposing Disputed Statements on the Web

### 2009-03-30 papers/uist_thinklink/thinklink.tex
Did another pass over the paper. Now have a half-page spare for filling with more figures.

\abstract
Think Link is a tool that helps a user know when information they read on a web page is disputed. As a user browses the web, Think Link highlights snippets of text that make claims that conflict with information on other web sites. If a user clicks on a highlighted snippet, Think Link will display an argument graph showing the best evidence for and against the claim the snippet is making.

Users provide all Think Link's information: they create new claims, mark new snippets, connect claims and snippets together.
Think Link is designed to support two primary usage scenarios: (i) Activists care strongly about a particular issue and combine Think Link with a search engine to find and mark snippets that make claims that they disagree with; and (ii) Sceptical Readers install Think Link as a browser extension to see when statements they read are disputed and find other sources tha tpresent alternative viewpoints.

@@

The web contains a huge amount of information, but some web sites contain innaccurate information~\cite{Mintz2002,Neumann2003,Resnik1998,Zhou2004} and some present only one side of a contentious issue~\cite{Herman2002,Gentzkow2007}. 
If a user is to gain a broad understanding of a topic then they will need to either stick to sources that they trust to provide accurate and balanced information or spend time looking for information on other web sites that conflicts with what they have read. 
Even if a user tries to be careful they can still be caught out by claims that they had not realized were disputed.
\todo{word this better}\todo{update all screenshots}

In this paper we present Think Link, a tool that helps users discover when information they read is disputed, and helps users find sources with alternative points of view. When Think Link is used as a browser plugin it will highlight snippets of text that makes disputed claims (Figure~\ref{highlight}). When a user clicks on a highlighted snippet, Think Link presents them with an argument graph that shows the best evidence for and against the claim (Figure~\ref{claimview}).

@@

Think Link relies on users to identify disputed claims, to find instances of these claims on web sites, and to vote for which sources provide the best support or opposition for a claim. 
Think Link is designed to cater to two primary usage scenarios:

\begin{description}
\item[Activists] care strongly about particular issues. They use Think Link to find and mark instances of claims that this disagree with so that other readers will see that these claims are disputed and be exposed to the opposing point of view.

\item[Sceptical Readers] want to know when information they read is disputed. They install Think Link as a browser plugin so that it will highlight disputed claims and show them the best evidence supporting opposing points of view.
\end{description}

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=5cm]{../screenshots/v2_popup_dim.png}
	\caption{Click on a claim to investigate evidence for and against it}
	\label{claimview}
	\end{center}
\end{figure}

@@

Think Link builds on work in several different areas. The argumentation structure is influenced by IBIS~\cite{Rittel1973} tools such as gIBIS~\cite{Conklin1987a}. The idea of highlighting potentially unstrustworthy information was applied to Wikipedia by WikiTrust~\cite{Adler2008a}. Tagging Systems~\cite{Marlow2006} influenced the way Think Link uses the community to collect and filter information. Clipping tools such as Internet Scrapbook~\cite{Sugiura1998} allow users to mark snippets on web sites.

What makes Think Link interesting is the way that it combines ideas from these different domains and applies them to the task of showing users when the information they read conflicts with information from other sources.
\todo{rewrite this?}

@@

Think Link's argument graph is inspired by Issue Based Information System (IBIS)~\cite{Rittel1973} tools such as gIBIS~\cite{Conklin1987a}, Compendium~\cite{Selvin2001}, Zeno~\cite{Gordon1997}, and Cohere~\cite{Shum2008}. IBIS tools model debate as a graph of connected issues, positions, and arguments. While the graph structure varies between tools, most tools allow a node to support or oppose another node and allow a node to be linked to an issue.

Although Think Link's argument graph is very similar to that used by IBIS tools, it uses it for a different purpose. In Think Link the focus is on the snippets, and the purpose of the argument graph is to organize snippets, identify when snippets are disputed, and identify which snippets provide the best evidence for a particular point of view. A user is encouraged to create a new claim only when they want to group together a large number of snippets that make that claim. A Think Link user is expected to form an opinion primarily by looking at the snippets listed as evidence, rather than by looking at the argument graph itself. This differs from the normal way in which previous IBIS tools have been used. In a tool such as gIBIS~\cite{Conklin1987a}, the focus is on the argument graph. A user is encouraged to break their argument down into as many separate ideas as possible and users are expected to use the graph itself to reach a conclusion. In Think Link it is perfectly acceptable to have a claim that is not linked to any other claims or topics, but is associated with many snippets --- this would not fit with the expected usage model for other IBIS tools.

Isenmann and Reuter~\cite{Isenmann1997} identify a number of problems with using IBIS tools to help people resolve disputes and make decisions. Broadly speaking, they found that opposing groups were unkeen to agree to use an IBIS tool to resolve their disputes, and that users found it difficult to properly encode a complex issue as an argument graph. We believe that while the problems they observe are important when an IBIS tool is being used for conflict modelling and conflict resolution, they are less of a problem for a tool like Think Link that is designed primarily for conflict discovery.

Cohere~\cite{Shum2008} allows a user to specify one or more URLs as evidence when creating a new claim and provides a Firefox plugin to help a user create a claim based on the page they are browsing; Cohere works with URLs rather than snippets and does not allow one to associate a new URL with an existing claim written by someone else. Cohere is not designed to be used to identify snippets on web pages that make disputed claims.

@@

Think Link's argument visualization is influenced by the left-to-right layout of Cohere~\cite{Shum2008}. Compendium~\cite{Selvin2001} contains a number of other visualizations of argument graphs. Mess Maps~\cite{Horn2007} present an alternative view in which an argument is divided into different sectors, each of which presents the argument from a different frame of discourse (e.g. policy maker vs industrialist vs environmentalist).

@@

If one sees a claim on the web that one suspects might be untrue then one can look it up on Snopes\footnote{http://snopes.com} or FactCheck\footnote{http://factcheck.org}. Snopes is a database of urban legends that the site owners investigated to determine whether they are true. 
Think Link's database automatically imports all contentious claims identified by Snopes.
FactCheck is a web site that investigates claims being made by US political parties and attempts to uncover the facts.

%FactCheck updates infrequently enough that we have been able to manually add its disputed claims to Think Link as they appear.

NewsCube~\cite{Park2009} and MediaCloud\footnote{http://mediacloud.org} use statistics to help readers avoid media bias. NewsCube presents a user with articles on the same topic that have different biases. MediaCloud applies various statistical analyses to news sources so that a reader can see when different news sources associate different words with the same topic.

Several authors have investigated ways to make Wikipedia\footnote{http://wikipedia.org} more trustworthy. WikiTrust~\cite{Adler2008a} highlights passages on wikipedia based on the likelihood that another user will change that text in the future --- recent edits by untrusted editors are marked as less trustworthy than old edits by trusted editors. Wiki Dashboard~\cite{Kittur2008} presents the reader of a Wikipedia article with a visualization that shows them how it has been edited in the past and lets them see graphically how contentious the topic is. Wiki Scanner\footnote{http://wikiscanner.virgil.gr} finds Wikipedia edits that have been made by people with an interest in spreading misinformation (e.g. people from a company editing pages about that company).

@@

Annotation tools~\cite{Marshall1998} such as Annotea~\cite{Koivunen2001} and ScreenCrayons~\cite{Olsen2004} allow users to highlight sections of text on a page. Annotation systems often also do clipping. Clipping tools such as Internet Scrapbook~\cite{Sugiura1998}, Hunter Gatherer~\cite{Schraefel2002}, ScratchPad~\cite{Gotz2007}, ClipMarks\footnote{http://clipmarks.com}, and Diigo\footnote{http://diigo.com} allow users to collect text snippets from web pages, tag them, and share them with friends. In some cases, other users who see a web page an see text highlighted where other users have clipped it. These tools do not attempt to identify when snippets make disputed claims or to connect them to opposing sides of an argument.

ClaimSpotter~\cite{Sereno2005,Sereno2004} allows one to mark up a scholarly paper with logical triples (subject, verb, object) describing interesting claims that are being made in the document. This semantic information can be used to connect claims in different documents. Entity Workspace~\cite{Bier2006} does something similar for intelligence documents. Unlike Think Link, these tools are looking for logical relations between entities rather than instances of already-known claims.

SpinSpotter\footnote{http://spinspotter.com} allows a user to highlight snippets of text that contain spin or bias and either describe why the text is biased, or rewrite the text in an unbiased way. While SpinSpotter and Think Link share a goal of drawing user attention to biased or inaccurate information, they do so in a different way. SpinSpotter annotates a snippet with an annotation specific to that particular snippet of text, while Think Link treats a snippet as being an instance of a shared contentious claim, and links all snippets identified as making that claim to a shared graph node linking to other information about that claim.

Videolyzer~\cite{Diakopoulos2008}\footnote{http:\\www.videolyzer.com} allows users to annotate and comment on political videos with accompanying textual transcriptions. A user can mark up a section of video for bias, accuracy, or rhetorical technique. Comments can include references to external sources that back up the argument being made. Like SpinSpotter, Videolyzer attaches annotations to a specific video section and does not attempty to gather multiple video sections that make a common contentious claim.

@@

Several tools layer an alternative navigation graph over information on the web. TextRunner~\cite{Etzioni2008} and Idea Navigation~\cite{Etzioni2008} look for instances of subject-verb-object triples on web pages and connect these together as a graph in which objects are linked by statements made about them on different web pages. ScentHighlights~\cite{Chi2005a} highlights snippets of text that relate to topics the user has expressed interest in. Kolak and Schillit~\cite{Kolak2008} detect cases where one book has quoted from another one, and use this to create links between books. This ``linking of quotations'' is similar in spirit to the linking of claims in Think Link.

@@

Think Link is designed to be used in two different ways. Sceptical wish to be alerted when information they read on the web conflicts with information on other web sites. Activists scour the web for web sites that make claims that they disagree with so that they can draw the attention of sceptical readers to claims that they disagree with. The same user may act as a sceptical reader sometimes and an activist at other times.

@@

If a sceptical reader has installed the Think Link browser extension, Think Link will draw the users attention to text snippets that make or imply disputed claims by highlighting them in red (Figure~\ref{highlight}). If a user hovers their mouse over a highlighted snippet then Think Link displays a tooltip giving the disputed claim. Clicking on a highlighted snippet reveals a visualization showing the best evidence for and against the claim, as determined by the user community (Figure~\ref{claimview}).

@@

\todo{ignore button}
\todo{talk about the margin?}

@@

In our user studies, we found that sceptical readers wanted to be able to investigate the evidence for and against a claim without having to navigate away from that claim. We thus created an interface that consists of a horizontal array of panels where each panel provides information about the item that is selected in the panel to its left. If a panel describes a disputed claim (Figure~\ref{panel}), then a user can investigate a particular piece of supporting evidence by clicking on it and looking at the information in the panel to the right. 
To emphasize the connection between the panels, the claim browser places an arrow next to each selected item, pointing to the panel that gives more information about that item.

The panel for a claim (Figure~\ref{panel}) lists evidence that will help a user decide whether the claim is true. Evidence is categorized as either supporting, opposing, or being related-to the claim. The ``related-to'' category is used for evidence that does not fit neatly into one side of the argument. Evidence can either be a snippet that talks about that claim, or another claim whose truth would support or oppose this claim.

@@

To preserve visual consistency, Think Link uses the same claim browser interface for the small popup interface as for the full-window interface. When used as a popup browser, the interface shows only one panel. Clicking on an item in the panel scrolls the display to the right to reveal a new panel in a manner similar to Apple's iPhone. If the user clicks the ``back'' button, the interface will quickly scroll left back to the previous panel.

@@

Think Link's claim graph is a variant of the IBIS~\cite{Rittel1973} model. There are three types of node: snippets, claims, and topics. A snippet is a region of text taken from a web page; a claim is a statement about the world or position that one can take on some issue; and a topic is an issue or concept that a claim might relate to.. Nodes are connected together by typed, directed, links. There are three link types: supports, opposes, and relates-to. A snippet or claim can support, oppose, or relate-to a claim; and any node can relate-to a topic.

Think Link uses topics to group together related claims. A topic may be an issue that several claims are proposing solutions for, for example ``What should we do about global warming?''. Alternatively, it can be something claims are about, for example ``Carbon Dioxide''. Think Link uses the list of page titles on Wikipedia as a seed-set for its topics and users can also add new topics from within the claim browser.

Think Link's graph model is a simpler than that used by gIBIS~\cite{Conklin1987}: we don't distinguish between an argument and a position, we allow a claim to relate-to another claim without supporting or opposing it, we merge issues with topics, we collapse gIBIS's five ways of connecting issues together and four ways of connecting a claim to an issue into a single relates-to relation. While Think Link's simplified graph structure is arguably less useful for the argument modelling and resolution task that gIBIS was designed for, it is sufficient for the conflict discovery and snippet organization task that Think Link's graph is intended for, and we have found that the smaller set of less precise link and node types reduces the mental effort required to create an argument graph.

The order in which evidence is displayed is determined by user voting. A user can vote for or against a particular piece of evidence by clicking on the voting button next to that item~(Figure~\ref{voting}). When a user looks at a list of evidence they will see first the things they voted for and then the other evidence ordered based on the number of votes it received from other users.

One danger in a voting system is that a large group of people will drown out the opinions of their opponents by voting down their opinions. Think Link uses several strategies to try to avoid this happening. Firstly, positive votes count for more than negative votes. Thus if two different groups are voting up their own evidence and voting down the opposing group's evidence, it is still likely that the opinions of both groups will be relatively prominent. Secondly, a piece of evidence only competes against other pieces of evidence on the same side of the argument, thus even if supporters of one side are voting up their own evidence, this will not push down evidence on the other side. In some cases, it may still be necessary to introduce a moderation system similar to that used in Wikipedia, where trusted users can override popular opinion when things go wrong.

@@

If a user has installed the Think Link browser extension then they can create a snippet from text on a web page by selecting the text and selecting either ``This is disputed'' or ``This is interesting'' from the context menu. A user selects ``This is disputed'' if they believe that readers of that snippet should be alerted of the fact that a claim that that snippet is making or implying is disputed. A user selects ``This is interesting'' if they believe that the snippet contains useful evidence that could be for readers investigating a disputed claim.

@@

Think Link does not require that a user associate a snippet with a claim at the point at which they create it. Instead, Think Link encourages a user to associate snippets with claims and topics ``in bulk'' using the claim browser interface, after they have gathered many snippets. 
One anticipated usage scenario for Think Link is an activist user who uses a search engine to find a large number of snippets that make a claim that they disagrees with. 
In this case, the user can save time by first collecting all their snippets, and then attaching all their snippets to their disputed claim in bulk.

@@

@@

\item[Immediate:] A user can select a claim for a snippet that they have just marked. When a user marks a snippet, Think Link will initially highlight it in blue to show the user that the snippet is not currently associated with a claim or topic and will not be shown to other users. If the user clicks on the highlighted snippet, then Think Link will bring up the same suggestion panel used in the ``snippet first'' method.
\end{description}

Think Link uses the same suggestion system to suggest connections between claims. It is important to make sure that the argument graph stays well connected as it grows. If users create duplicate claims or don't connect their claims to existing claims then then graph becomes less useful. Think Link tries to make it easy for users to keep the claim graph well connected by suggesting claims that should be linked together and allowing a user to enable a suggested connection with a single click.

When gathering ``interesting'' snippets, a user may want to associate a snippet with a general topic rather than a specific claim. It is only necessary to associate an ``interesting'' snippet with a claim when a user wants to use it as evidence for a particular claim. In some cases a user will gather snippets that they might want to use later, but without concrete plans for how they might want to use them or what claims they might want to use them as evidence for. In such cases, it is easier to file the interesting snippets under a general topic and possibly attach them to a claim some time in the future.

Think Link uses the Wikify algorithm~\cite{Mihalcea2007} to suggest topics for snippets or claims. The Wikify algorithm imagines that a piece of text was on a Wikipedia page and predicts what pages that text would most likely link to based on the probability that any particular n-gram links to any particular page. Recall that the set of Think Link topics is seeded with the set of Wikipedia page titles. The Wikify algorithm performs significantly better than a word-frequency comparison as it biases towards topics that are heavily linked to.

Even with these suggestion and bulk connection features, gathering snippets that make a disputed claim or provide useful evidence requires a non-trivial amount of work. Fortunately, several activist users we talked to told us that they already spend a lot of time performing similar tasks; currently they search for web pages about issues they care about and respond to disputed claims by posting comments or talking about them on their own blog. Some users use tools like Google Alerts\footnote{http://www.google.com/alerts} to be notified every time a new page appears about the issue they are interested in. Moreover, although it would not be practical for activists to mark up all pages on the web, web page popularity follows a Zipf law~\cite{Krashkov2006}, and so one can achive useful coverage by only marking up the relatively small number of very popular pages (for example articles on major news sites).

@@

Think Link consists of a browser extension, a page annotation script, a shared public database of contentious claims, and a web-based argument interface that allows one to explore and manipulate the claim graph. These four components are largely independent of each other and talk to each other using an open API that can also be used by other tools. Indeed the settings panel for the browser extension allows a user to tell it to bind to alternative versions of the other modules.

The page annotation script is a javascript file that can be included into any HTML page. When it is run on a page it sends the page URL to the server, asking it to send back information about any contentious snippets on that page. If any such snippets are found, the page modification script highlights them in red. If the user clicks on a highlighted snippet then it shows an iframe containing a visualization from whatever visualization server it has been configured to use.

The only purpose of the browser extension is to insert the page modification script onto every page that the user loads. The browser extension is not the only way that one can access Think Link highlights. One can get the same effect by browsing through a proxy (like WBI~\cite{Barrett1997}), or if the owner of a web site included the page annotation script themselves.

Think Link's annotation system has some privacy issues. Every time the user browses to a page, the URL is sent to the Think Link server to check whether there are any known annotations for that page. 
Think Link reduces privacy issues by not sending cookies or other identifying information, and Think Link's requests can be cached by a third-party proxy if desired. 
In future work we hope to reduce these privacy issues. One possibility is to use a hashing system similar to that used by Google Safe Browsing\footnote{http://code.google.com/p/google-safe-browsing/}.

The protocol used by the Think Link server is an open REST API that other tools are free to use. We are also considering supporting one or more of the several argumentation interchange formats that have been proposed ~\cite{Rahwan2007a,McGinnis2007}.

@@

The aim of the first study was to see how users normally browse the web and see their reactions to an early version of the Think Link argument graph. The aim of the second study was to evaluate user responses to an updated version of the interface and evaluate how users responded to seeing highlighted snippets on the page. At the end of each study, we asked each partipicant whether there were times in the past where they would have wanted to use Think Link. We present the results of the two studies together.

@@

Many users would consistently mark the first paragraph of an article as a snippet. This paragraph would frequently summarize the arguments made in the rest of the document document and often made an important claim that other claims in the document supported or provided context for.

@@

Many participants expressed a desire to organize claims into connected arguments during their session.

>>>>

\abstract
Think Link is a tool that helps users know when information they read on a the web is disputed. As a user browses the web, Think Link highlights snippets of text that make claims that users have identified as being disputed. If a user clicks on a highlighted snippet, Think Link will display an argument graph showing the best evidence for and against the claim the snippet is making.

Users provide all of Think Link's information: they create new claims, mark new snippets, connect snippets to claims, and vote for the best evidence.
Think Link is designed to support two primary usage scenarios: (i) Activists care strongly about a particular issue and combine Think Link with a search engine to find and mark snippets that make claims that they disagree with; and (ii) Sceptical Readers install Think Link as a browser extension to see when statements they read are disputed and find other sources tha tpresent alternative viewpoints.

@@

The web contains a huge amount of information, but some of this information is incorrect~\cite{Neumann2003,Resnik1998,Zhou2004} and some sites present only one side of a contentious issue~\cite{Herman2002}. 
If a user is to gain a broad understanding of a topic then they will need to either spend time looking for alternative points of view, or restrict themselves to sources that they believe they can trust to provide accurate and balanced information.
Even if a user tries to be careful, they can still be caught out by claims that they had not realized were disputed.
\todo{word this better}\todo{update all screenshots}

In this paper we present Think Link, a tool that helps users discover when information they read is disputed, and helps users find sources with alternative points of view. If a user has installed the Think Link browser extension hen it will highlight snippets of text on the web that make disputed claims (Figure~\ref{highlight}). When a user clicks on a highlighted snippet, Think Link presents them with an argument graph that shows the best evidence for and against the claim (Figure~\ref{claimview}).

@@

Think Link relies on users to identify disputed claims, to find instances of these claims on web pages, and to vote for the sources that provide the best support or opposition for a claim. 
Think Link is designed to cater to two primary usage scenarios:

\begin{description}
\item[Activists] care strongly about particular issues. They use Think Link to mark snippets that make claims that they disagree with. They are motivated by a desire to make other readers see that these claims are disputed and learn about the opposing point of view.

\item[Sceptical Readers] want to know when information they read is disputed so that they can avoid being misled. They install Think Link as a browser plugin so that it will highlight disputed claims and show them opposing points of view.
\end{description}

The same user may be an Activist for some issues and a Sceptical Reader for others.

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=5cm]{../screenshots/v2_popup_dim.png}
	\caption{Click on a snippet to investigate evidence for the claim it makes}
	\label{claimview}
	\end{center}
\end{figure}

@@

Think Link builds on prior work in several different areas. The argument graph is influenced by IBIS~\cite{Rittel1973} tools such as gIBIS~\cite{Conklin1987a}. The idea of highlighting potentially unstrustworthy information was applied to Wikipedia by WikiTrust~\cite{Adler2008a}. Tagging Systems~\cite{Marlow2006} influenced the way Think Link uses the community to collect and filter information. Think Link's snippets are influenced by clipping tools such as Internet Scrapbook~\cite{Sugiura1998}.

What makes Think Link interesting is the way that it applies ideas from these different domains to the task of helping users deal with misinformation and bias on the web.

@@

Think Link's argument graph is inspired by IBIS\footnote{Issue Based Information System}~\cite{Rittel1973} tools such as gIBIS~\cite{Conklin1987a}, Compendium~\cite{Selvin2001}, Zeno~\cite{Gordon1997}, and Cohere~\cite{Shum2008}. IBIS tools model debate as a graph of issues, positions, and arguments. While the graph structure varies between tools, most tools allow a node to support or oppose another node and allow a node to be linked to an issue.

Cohere~\cite{Shum2008} allows a user to specify one or more related URLs when creating a new claim, and provides a Firefox plugin to help a user create a claim about a web page they are reading. Unlike Think Link, Cohere is not designed to be used to alert users about disputed snippets. Cohere works with URLs rather than snippets and does not allow one to connect a new URL to an existing claim created by someone else.

Although Think Link's argument graph is similar to that used by IBIS tools, it uses it for a different purpose. In Think Link the focus is on snippets, and the argument graph is used to organize snippets, identify when snippets are disputed, and identify which snippets provide the best evidence for a particular claim. A user is expected to create a new claim only when they want to group together several snippets that make that claim. A Think Link user is expected to form an opinion primarily by looking at the snippets and the pages they are part of, rather than by looking at the argument graph itself. By contrast, in an IBIS tool such as gIBIS~\cite{Conklin1987a}, the focus is on the argument graph. A gIBIS user is encouraged to break their argument down into as many separate ideas as possible and is expected to use the graph itself to reach a conclusion. In Think Link it is perfectly acceptable to have a claim that is not linked to any other claims but is associated with many snippets.

Isenmann and Reuter~\cite{Isenmann1997} identified a number of problems with using IBIS tools to help people resolve disputes and make decisions. Broadly speaking, they found that opposing groups were unkeen to agree to use an IBIS tool to resolve their disputes, and that users found it difficult to properly encode a complex issue as an argument graph. We believe that while the problems they observe are important when an IBIS tool is being used for conflict modelling and conflict resolution, they are less of a problem for a tool like Think Link that is designed for identifying snippets that represent conflicting points of view.

@@

@@

If one sees a claim on the web that one suspects might be untrue then one can look it up on Snopes\footnote{http://snopes.com} or FactCheck\footnote{http://factcheck.org}. Snopes is a database of urban legends that the site owners investigated to determine whether they are true. 
Think Link's database automatically imports all contentious claims identified by Snopes.
FactCheck is a web site that investigates claims being made by US political parties and attempts to uncover the facts. We use Fact Check as a useful source of disputed claims.

% FactCheck updates infrequently enough that we have been able to manually add its disputed claims to Think Link as they appear.

\todo{Make sure we stay in sync}

NewsCube~\cite{Park2009} and MediaCloud\footnote{http://mediacloud.org} use statistics to help readers avoid media bias. NewsCube finds articles on the same topic that have different biases. MediaCloud shows which different words different news sources associate with the same topic.

Several authors have created tools that help users know when to trust information on Wikipedia\footnote{http://wikipedia.org}. WikiTrust~\cite{Adler2008a} highlights passages on wikipedia that have been written recently or written by untrusted editors. Wiki Dashboard~\cite{Kittur2008} creates a visualization of the edit history of a Wikipedia article that lets a user see how contentious it is. Wiki Scanner\footnote{http://wikiscanner.virgil.gr} finds cases where a Wikipedia edit has been made by someone with a conflict of interest.

@@

Annotation tools~\cite{Marshall1998} such as Annotea~\cite{Koivunen2001}, ScreenCrayons~\cite{Olsen2004}, and ReframeIt\footnote{http://reframeit.com} allow users to highlight sections of text on a page. Clipping tools such as Internet Scrapbook~\cite{Sugiura1998}, Hunter Gatherer~\cite{Schraefel2002}, ScratchPad~\cite{Gotz2007}, ClipMarks\footnote{http://clipmarks.com}, and Diigo\footnote{http://diigo.com} allow users to collect text snippets from web pages, tag them, and share them with friends. Some tools highlight snippets that have been clipped by other users. These tools do not attempt to identify when snippets make disputed claims or to connect them to opposing sides of an argument.

SpinSpotter\footnote{http://spinspotter.com} allows a user to mark snippets that contain spin or bias. A user can comment on why a snippet is biased and rewrite the snippet in a neutral way. While SpinSpotter and Think Link both draw attention to biased or inaccurate snippets, they do different things with the snippets. SpinSpotter lets users annotate a snippet with comments specific to that particular snippet, while Think Link treats a snippet as being an instance of a shared claim, and links all snippets identified as making that claim to a shared node in the argument graph that is linked to other points of view.

Videolyzer~\cite{Diakopoulos2008}\footnote{http:\\www.videolyzer.com} allows users to annotate and comment on political videos. A user can attach a comment to a section of video and tag it for bias, accuracy, or rhetorical technique. Comments can include references to external sources that back up the argument being made. Like SpinSpotter, Videolyzer does not attempty to gather multiple video sections that make a common contentious claim.

ClaimSpotter~\cite{Sereno2005,Sereno2004} allows one to mark up a scholarly paper with logical subject-verb-object triples describing important claims made in the document. Entity Workspace~\cite{Bier2006} does something similar for intelligence documents. Like Think Link, these tools allow a user to mark the claims being made in a document, however these tools are more formal and are designed to extract knowledge rather than informally mark disputed snippets.

@@

Several tools layer an alternative navigation graph over information on the web. TextRunner~\cite{Etzioni2008} and Idea Navigation~\cite{Etzioni2008} look for instances of subject-verb-object triples on web pages and connect these together as a graph in which objects are linked by statements made about them on different web pages. ScentHighlights~\cite{Chi2005a} highlights snippets of text that relate to topics the user has expressed interest in. Kolak and Schillit~\cite{Kolak2008} detect cases where one book has quoted from another one, and use this to create links between books.

@@

For Sceptical Readers, Think Link highlights disputed snippets and links them to snippets on other web sites that present alternative points of view. For Activists, Think Link makes it easy for users to mark snippets about issues they care about and connect them into an argument graph.

@@

If a sceptical reader has installed the Think Link browser extension, Think Link will draw attention to snippets that make or imply disputed claims by highlighting them in red (Figure~\ref{highlight}). If a user hovers their mouse over a highlighted snippet then Think Link displays a tooltip giving the disputed claim. Clicking on a highlighted snippet reveals a visualization showing the best evidence for and against the claim, as determined by the user community (Figure~\ref{claimview}).

@@

Normally Think Link will only highlight snippets that make disputed claims that the user has not asked to ignore, and snippets marked by the user themselves. If the user wants to see all snippets on a page then they can do so by opening the Think Link sidebar.

\todo{ignore button}
\todo{talk about the margin?}
\todo{Talk about snippet and topic previewing}

@@

In our user studies, we found that sceptical readers wanted to be able to investigate the evidence for and against a claim without having to navigate away from that claim. We thus created an interface that consists of an expanding horizontal array of panels where each panel provides information about the item that is selected in the panel to its left. If a user clicks on a link in a panel then a new panel opens to the right giving more information about the linked node. To emphasize the connection between the panels, the claim browser places an arrow next to each selected item, pointing to the panel that gives more information about that item.

The panel for a claim (Figure~\ref{panel}) lists evidence that will help a user decide whether the claim is true. Evidence is categorized as either supporting, opposing, or being related-to the claim. The ``related-to'' category is used for evidence that does not fit neatly into one side of the argument. Evidence can either be a snippet that talks about that claim, or another claim whose truth would support or oppose this claim.  The panel for a snippet shows the snippet text in the context of the web page it is part of. This, combined with the cascading panel interface allows a user to quickly read the evidence for and against a claim without having to leave the claim browser interface.

\todo{Remove ``related`` fom the topics list - confuses with related claims}
\todo{Show the other panels?}

@@

To preserve visual consistency, Think Link uses the same claim browser interface for the small popup interface as for the full-window interface. When used as a popup browser, the interface shows only one panel. Clicking on an item in the panel scrolls the display to the right to reveal a new panel. If the user clicks the ``back'' button, the interface will quickly scroll left back to the previous panel.

@@

Think Link's claim graph is a variant of the IBIS~\cite{Rittel1973} model. There are three types of node: snippets, claims, and topics. A snippet is a region of text taken from a web page; a claim is a statement about the world or a position that one can take on some issue; and a topic is an issue that a claim might address or a thing that a claim might be about. Nodes are connected together by typed, directed, links. There are three link types: supports, opposes, and relates-to. A snippet or claim can support, oppose, or relate-to a claim; and any node can relate-to a topic.

Think Link uses the list of page titles on Wikipedia as a seed-set for its topics. This allows Think Link to use the Wikify~\cite{Mihalcea2007} algorithm to automatically suggest topics for snippets and provides us with a comprehensive ready-made set of topics with well-maintained descriptions and synonyms.

Think Link's graph model is a simpler than that used by gIBIS~\cite{Conklin1987}: we don't distinguish between an argument and a position, we allow a claim to relate-to another claim without supporting or opposing it, we merge issues with topics, and we collapse gIBIS's five ways of connecting issues together and four ways of connecting a claim to an issue into a single relates-to relation. While Think Link's simplified graph structure is arguably less useful for the argument modelling and resolution task that gIBIS was designed for, we have found that it is sufficient for the conflict discovery and snippet organization task that Think Link's is designed for, and we have found that the smaller set of less precise link and node types reduces the mental effort required to create an argument graph.

The order in which evidence is displayed is determined by user voting. A user can vote for or against a particular piece of evidence by clicking on the voting buttons next to that item~(Figure~\ref{voting}). When a user votes for something it will be moved to the top of their list, and also make that item earlier for other users.

One danger in a voting system is that a large group of people may drown out the opinions of their opponents by voting down their opinions. Think Link uses several strategies to try to avoid this happening. Firstly, positive votes count for more than negative votes. Thus if two different groups are voting up their own evidence and voting down the opposing group's evidence, it is still likely that the opinions of both groups will be relatively prominent. Secondly, a piece of evidence only competes against other pieces of evidence on the same side of the argument, thus even if supporters of one side are voting up their own evidence, this will not push down evidence on the other side. In some cases, it may still be necessary to introduce a moderation system similar to that used in Wikipedia, where trusted users can override popular opinion when things go wrong.

@@

If an Activist has installed the Think Link browser extension then they can create a snippet by selecting text on a web page and selecting either ``This is disputed'' or ``This is interesting'' from the context menu (Figure~\ref{createprocess}). A user selects ``This is disputed'' if they believe that readers of that snippet should be alerted that the snippet is making a claim that is disputed. A user selects ``This is interesting'' if they believe that the snippet contains useful evidence that could be useful for readers investigating a disputed claim.

@@

Think Link does not require a user to specify the disputed claim a snippet is making at the point at which they mark it. Instead, Think Link encourages a user to gather many snippets and then use the claim browser interface to associate claims with snippets in bulk.
One anticipated usage scenario for Think Link is an activist user who uses a search engine to find a large number of snippets that make a claim that they disagree with. 
In this case, the user can save time by first collecting all their snippets, and then attaching all their snippets to their disputed claim together.

@@

\todo{Updated screenshot with ``enter new claim or search keywords'' present}

@@

\item[Immediate:] A user can select a claim for a snippet that they have just marked. When a user marks a snippet, Think Link will initially highlight it in blue to show that the snippet is not currently associated with a claim or topic and will not be shown to other users. If the user clicks on the highlighted snippet, then Think Link will bring up the same suggestion panel used in the ``snippet first'' method.
\end{description}

Think Link uses the same suggestion system to suggest connections between claims. It is important to make sure that the argument graph stays well connected as it grows. If users create duplicate claims or don't connect their claims to existing claims then then graph becomes less useful. Think Link tries to make it easy for users to keep the claim graph well connected by suggesting claims that should be linked together and allowing a user to create a suggested connection with a single click.

When gathering ``interesting'' snippets, a user may not yet know what argument they might want to use the snippet to support, or even whether they want to use it at all. In such cases the user can either leave the snippet unfiled until they thing of something to use it for, or attach it to a topic in the hope that another user might find it useful.

Think Link uses the Wikify algorithm~\cite{Mihalcea2007} to suggest topics for snippets or claims. The Wikify algorithm imagines that a piece of text was on a Wikipedia page and predicts what pages that text would most likely link to based on the probability that any particular n-gram links to any particular page. Recall that the set of Think Link topics is seeded with the set of Wikipedia page titles. The Wikify algorithm performs significantly better than a word-frequency comparison as it biases towards topics that are heavily linked to. Connecting claims and snippets to topics makes it easier to find other claims and snippets that might be related.

\todo{Talk about previewing a topic by showing wikipedia page}

Even though Think Link tries to make creating and linking snippets as easy as possible, it still requires a non-trivial amount of work. Fortunately, several activist users we talked to told us that they already spend a lot of time performing similar tasks; currently they search for web pages about issues they care about and respond to disputed claims by posting comments or talking about them on their own blog. Some users use tools like Google Alerts\footnote{http://www.google.com/alerts} to learn when a new page appears about an issue they are interested in. Moreover, although it would not be practical for activists to mark up all pages on the web, web page popularity follows a Zipf law~\cite{Krashkov2006}, and so one can achieve useful coverage by only marking up the relatively small number of very popular pages (for example major news sites).

@@

Think Link consists of a browser extension, a page annotation script, a shared database server, and a web-based claim browser interface. These four components are largely independent of each other and talk to each other using an open API that can also be used by other tools.

The page annotation script is a javascript file that can be included into any HTML page. When it is run on a page it sends the page URL to the server, asking it to send back any snippets on that page. There are of course privacy issues here since this could allow user browsing to be tracked. We reduce this problem a little by not sending cookies or other identifying information, and making the protocol cacheable. In future we hope to device a way to reduce concerns further. One idea we are exploring is to use hashing similar to that used by Google Safe Browsing\footnote{http://code.google.com/p/google-safe-browsing/} to identify pages that might contain disputed information and then requiring a user to explicitly enable Think Link for particular sites for Think Link will request disputed snippets.

The browser extension inserts the page annotation script onto every page the browser loads. One can get the same affect by browsing through a proxy or if the page included directly by the page author.

%The protocol used by the Think Link server is an open REST API that other tools are free to use. In the future, the server may support one or more of the argumentation interchange formats that have been proposed~\cite{Rahwan2007a,McGinnis2007}.

@@

The aim of the first study was to see how users normally browse the web and see their reactions to an early version of the Think Link argument graph. The aim of the second study was to evaluate user responses to an updated version of the interface and evaluate how users responded to seeing highlighted snippets on the page. We present the results of the two studies together.

@@

Users would frequently mark the first paragraph of an article as a snippet. This paragraph would frequently summarize the arguments made in the rest of the document document and often made an important claim that other claims in the document supported or provided context for.

@@

Several participants expressed a desire to connect related claims during their session.
